\documentclass{beamer}

\title{Feedback - Marcus Chow}

\author{Jeppe Søndergaard Johansen (pcv439)}

\usetheme{Frankfurt}
\usecolortheme{orchid}

\begin{document}


\maketitle


\begin{frame}
\frametitle{Overview}

\begin{itemize}
    \item General Opinion
    \item structure
    \item Content/Analysis
    \item Application
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{General Opinion}

Good:

\begin{itemize}
    \item Good thorough valuation.
    \item Nice figures and graphs. Really helps with the reading experience.
    \item Good considerations about the valuation practices.
\end{itemize}

To be improved:

\begin{itemize}
    \item The paper is very thorough but you might consider trimming some of the part 5 and onwards. You get a little heavy with the text. Especially considering you still need analysis and conclusion to be written.
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Structure}

Good:

\begin{itemize}
    \item Your introduction outlines your analysis strategy.
    \item Good presentation of the company's activities.
    \item Nice Tables and figures!\end{itemize}

To be improved:

\begin{itemize}
    \item Use figures for your forecasts.
    \item Add a discussion where you consider the shortcomings of your valuation.
    \item you write ``analysts expect revenue to decrease by 2 - 3\%...'', which analysts has said that?
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Content/Analysis}

Good:

\begin{itemize}
    \item You seem very researched about considerations of valuation practices.
    \item Figure 6.1 is very good.
    \item You divide the strategic analysis into two parts: micro and macro.
    \item the Data of 2018 and 2019 are used for comparison in the the process to find the sensitivity to WACC.
\end{itemize}

To be improved:

\begin{itemize}
    \item you write electricity consumption is not dependent on macro economic development. How do you know?
    \item  long run nominal gdp growth 4,01 \% how do you settle on that value.
    \item In general the PEST analysis lacks data to confirm your hypothesis.
\end{itemize}

\end{frame}

\end{document}
